The error in Bayesian phylogenetic reconstruction when speciation is not instantaneous

### 2018-06-14 article.tex
Starting with different RNG seed is good enough

From each biological parameter set, we simulate a protracted birth-death tree,
using the PBD package (\cite{pbd}) in the R programming language (\cite{r}), 
all with a crown age of 15 million years as used in \cite{etienne2014}.
Each protracted birth-death tree uses a different random number
generator seed, which makes all runs independent, resulting in a balanced 
data set. \richel{Rampal assumed runs with close seeds were related. 
I assume I have convinced him otherwise]} \rampal{I am not saying that close seeds mean correlation; we simply don't know whether two lists of pseudo-random numbers generated from the two different seeds are not correlated, but perhaps the easiest way to resolve this is to check this for a fairly long list of numbers}\richel{(1) I checked reproducing one random number from two different (adjacent) seeds, see/run code below in comments. (2) I quote from https://stat.ethz.ch/R-manual/R-patched/library/base/html/Random.html: 'There is no guarantee that different values of seed will seed the RNG differently, although any exceptions would be extremely rare'. The full quote: 'set.seed uses a single integer argument to set as many seeds as are required. It is intended as a simple way to get quite different seeds by specifying small integer arguments, and also as a way to get valid seed sets for the more complicated methods (especially "Mersenne-Twister" [see below, ...]). There is no guarantee that different values of seed will seed the RNG differently, although any exceptions would be extremely rare. "Mersenne-Twister": From Matsumoto and Nishimura (1998). A twisted GFSR with period 2 to the power of 19937 - 1 and equidistribution in 623 consecutive dimensions (over the whole period). The 'seed' is a 624-dimensional set of 32-bit integers plus a current position in that set.'
(3) I've added a more elaborate example below that shows there is no overlapping sequence  
}
\RAMPAL{M.i. is het theoretisch nog niet evident, maar empirisch in orde, dus prima zo.}

% From Progress Report of week 21 2018, May 21 - May 25 2018:
% # If a random number if drawn with one seed,
% # how long until it is drawn by differently seeded
% # RNG?
%
% Pick any starting seed
% set.seed(2)
% value <- runif(n = 1)
%
% Pick any other seed
% set.seed(1)
% i <- 0
% while (value != runif(n = 1)) {
%   i <- i + 1
% }  
% print(i)

% More elaborate example:
% 
% # Goal:
% # Proof that runs with different RNG seeds result in completely different sequences
% 
% # SETUP
% n_seeds <- 10000
% sequence_length <- 10000
% 
% # START
% runs <- list()
% for (seed in seq(1, n_seeds)) {
%   set.seed(seed)
%   runs[[seed]] <- runif(n = sequence_length)
% }
% 
% numbers <- unlist(runs)
% duplicate_numbers <- numbers[duplicated(numbers)]
% 
% if (length(duplicate_numbers) == 0) {
%   print("all numbers are unique")
% } else {
%   percentage <- 100 * length(duplicate_numbers) / length(numbers)
%   print(paste(length(duplicate_numbers), "of", length(numbers), "numbers (", percentage ,"% ) occur multiple times"))
%   run_length_encoding <- rle(duplicated(numbers))
%   repeated_sequence_lengths <- run_length_encoding$lengths[ run_length_encoding$values == TRUE ]
%   longest_repeated_sequence <- max(repeated_sequence_lengths)
%   print(paste("Longest sequence of numbers that occurred multiple times (not necessarily in that same order) is", longest_repeated_sequence))
%   ggplot2::ggplot(
%     data.frame(length = repeated_sequence_lengths),
%     ggplot2::aes(x = length)
%   ) + ggplot2::geom_histogram(binwidth = 1) + ggplot2::coord_cartesian(ylim=c(0, 20)) +
%     ggplot2::ggtitle(
%       paste0(
%         "Lengths of sequence of numbers that occurred multiple times (not necessarily in that same order)\n",
%         "sequence length: ", sequence_length, ", n_seeds: ", n_seeds
%       )
%     )
%  }

>>>>

From each biological parameter set, we simulate a protracted birth-death tree,
using the PBD package (\cite{pbd}) in the R programming language (\cite{r}), 
all with a crown age of 15 million years as used in \cite{etienne2014}.
Each protracted birth-death tree uses a different random number
generator seed, which makes all runs independent, resulting in a balanced 
data set.
